\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-06-12 scam.tex
.
fixed the last merge

% Let $\inputsignal$ = $(t_0, u_0)$, $\ldots$, $(t_N,u_N)$ be a
% timed-sequence of inputs, where $t_0 = 0$, and for all $i > 0$, $t_i -
% t_{i-1} = \Delta$, and $u_i \in \Inputs$.  We can extend the forward
% simulation map to a sequence of states to describe the application of
% an input signal to excite the system as follows:
% $\simmap_\Delta(\initstate, \mathbf{u}) = \contState_N$, if for all $i
% \in [0,N-1]$, $\simmap_\Delta(\contState_i, u_i,t_i) =
% \contState_{i+1}$.
% 
% An alternative view of the forward simulation-map is as a
% parameterized reachability relation $\reach_\Delta{t,u} \subseteq
% \ContStates \times \ContStates$ defined as below:
% \[
% (\contState,\contState') \in \reach_\Delta{t,u}\text{ iff } \contState' = \simmap_\Delta(\contState,t,u).
% \]

% inputs modeling an embedded control system. 
% 
% we assume that the hybrid system is effectively a switched-mode
% dynamical system, \ie, the mode of the system is completely determined
% by its state.  An input to $\System$ is assumed to be a time-bounded
% {\em signal}, \ie, a function from $[0,T]$ to $\Inputs$, with $T$ as
% the time horizon, and $\Inputs \subseteq \Reals^k$.  In this paper, we
% view $\System$ as effectively black-box equipped with a forward
% simulation map, in a simulation time-step of $\Delta_t$ from time $t$,
% allows computing the unique reachable state $\vx \in \HybridStates$
% given state-input pair $(\vx,\vu)$.

% time and input parameterized reachability relation $\reach{t,
% \vu}_\System \subseteq \HybridStates \times \HybridStates$ as follows:
% $\simulate^{\System}:
% (\vx, \vu, t) \mapsto \vx$, where $\vx \in \HybridStates$, $\vu \in
% \Inputs$ and $t \in [0,T]$.

% Given the hybrid state space $\vx\in\HybridStates$ and input space $u
% \in\Inputs$ and time step $t$, it computes the unique successor state
% $\vy=\simulate^{\System}(\vx,u,t)$ such that $\vx \reach{t,u} \vy$.

% \begin{definition}[System Evolution]
%     The behavior of system $\System$ at time $t$ is described as an
%     evolution in the hybrid state-space $\HybridStates$ under the
%     effect of the input $\vu \in \Inputs$ at time $t$. The forward
%     simulation map $\mathsc{sim}^\System : \HybridStates \times \Inputs
%     \times \Reals^+ \mapsto \HybridStates$, maps a state $\x\in\HybridStates$ at time
%     $t$ to a new state $\x'\in\HybridStates$ at time $t+\Delta\in\Reals^+$, under a constant
%     input $\vu$.  Finally, we define the time and input parameterized
%     reachability relation $\reach{t,u} \subseteq \HybridStates \times
%     \HybridStates$ such that
%     \begin{equation}
%         (\vx,\vx') \in \reach{t,u} \;\text{iff}\; \vx'=\mathsc{sim}^{\System}(\vx,u,t).
%     \end{equation}
% \end{definition}

% \mypara{System Assumptions:} 
% We require that $\System$ can always be
% simulated forward in time with deterministic results. This in turn
% requires existence and uniqueness of trajectories over a finite time
% horizon $[0,T]$, which can be guaranteed by Lipschitz continuity of
% the vector field in each underlying hybrid mode, ruling away issues
% such as finite escape times~\cite{Meiss/2007/Differential}, and having
% well-defined semantics for simulations at switching boundaries. While
% these assumptions hold for the dynamical system examples which we
% consider in this paper, such assumptions can be restrictive for
% general control system models. When analyzing a system that does not
% obey theoretical conditions that allow deterministic simulation, we
% assume that the underlying tool used for numerical approximations of
% system behaviors uses deterministic simulation semantics.  Finally, we
% assume full observability of the system state, validate our results
% only against the $\mathsc{sim}^\System$ function (as the analytic closed-form
% representation of the system dynamics is assumed to be unavailable).
% From here on, we drop the subscript $\System$ whenever it is clear
% from the context. Also, to ease the presentation, we conflate the
% inputs with the state and denote them by $\vx$.
% 
\subsection{$\epsilon$-precision Transition System Abstraction}

@@

\inclfig[width=0.95\linewidth]{vdp_cont_traces.pdf}{Van der
Pol: continuous trajectories. Red and green boxes indicate unsafe and
initial sets.}{vdp-cont}
\inclfig[width=0.95\linewidth]{vdp_abs.pdf}{The discovered
$0.2$-TS abstraction. Red cells are unsafe cells and green cells are
initial cells.}{vdp-abs}

\begin{example} 
We now describe $\epsilon$-TS abstraction using the Van der Pol
oscillator benchmark from~\cite{zutshi2014multiple}. Simulations
generated using uniformly random samples are shown in
\figref{vdp-cont}. We want to check the property $P_3$, indicated by
the red box, given the initial set indicated by the green box. We
consider the $\epsilon$-TS abstraction defined by the quantization
function $\quant_{0.2}(\x)$. This results in an evenly gridded
state-space, where each cell is of size $0.2 \times 0.2$ units.
$\mathsf{ScatterAndSimulate}$ is then used to construct
$\TSAbstraction{0.2}{\System}$ using $2$ samples per cell and a time
step of $\Delta = 0.1s$. The complete process follows.  The
$\epsilon$-TS abstraction thus discovered is shown in
\figref{vdp-abs}. The red cells are unsafe and green cells are initial
cells.
\end{example}

% \mypara{Abstract}: Assume an implicit abstraction using the quantization
%         function $\quant_{\epsilon=0.2}(\x)$. The corresponding reachability
%     graph is $\scr{H}(\Delta=0.1)$.
% 
% \mypara{Discover}: Using scatter-and-simulate, enumerate a finite number
%     of cells (vertices) and the relations (edges) of the graph
%     $\scr{H}(0.1)$. Associate the set of generated trajectory
%     segments with their respective originating cells using a map $\ds:C
%         \mapsto \setof{(\vx,\vx') |\vx \in C}$.

@@

% \subsection{Example: Van der Pol Oscillator}
% \todo{Takes 4 iterations}
% \inclfig[width=0.90\linewidth]{vdp_disc_map.pdf}{Refinement of
% $\epsilon$-TS.}{vdp-map}
%

>>>>

\subsection{$\epsilon$-precision Transition System Abstraction}

@@

\inclfig[width=0.95\linewidth]{vdp_abs.pdf}{The discovered
$0.2$-TS abstraction. Red cells are unsafe cells and green cells are
initial cells.}{vdp-abs}
\begin{example}[Van der Pol Oscillator]~\label{ex:vdp}
We now describe $\epsilon$-TS abstraction using the Van der Pol
    oscillator benchmark from~\cite{zutshi2014multiple}. Simulations
    generated using uniformly random samples are shown in
    \figref{vdp-cont}. We want to check the property $P_3$:
    $x_{unsafe}\in[-1,-6.5]$ and $y_{unsafe}\in[-0.7, -5.6]$, given
    the initial set indicated $x0\in[-0.4, -0.4],\; y_0\in[0.4, 0.4]$.
    We consider the $\epsilon$-TS abstraction defined by the
    quantization function $\quant_{0.2}(\x)$. This results in an
    evenly gridded state-space, where each cell is of size $0.2 \times
    0.2$ units.  $\mathsf{ScatterAndSimulate}$ is then used to
    construct $\TSAbstraction{0.2}{\System}$ using $2$ samples per
    cell and a time step of $\Delta = 0.1s$. The complete process
    follows.  The $\epsilon$-TS abstraction thus discovered is shown
    in \figref{vdp-abs}. The red cells are unsafe and green cells are
    initial cells.
\end{example}

@@

% \subsection{Example: Van der Pol Oscillator}
% \todo{Takes 4 iterations}
% \inclfig[width=0.90\linewidth]{vdp_disc_map.pdf}{Refinement of
% $\epsilon$-TS.}{vdp-map}
%
\begin{example}
\inclfig[width=0.90\linewidth]{vdp_disc_map.pdf}{
Abstract trajectories discovered by $\mathsf{ScatterAndSimulate}$. Each
rectangle denotes a cell which is uniquely identified  by the
tuple against it.
%Cells and trajectory segments used by $1$-relational modeling.
}{vdp-abs-paths}

    Going back to the~\exref{vdp}, $\mathsf{ScatterAndSimulate}$ is able to
    find several abstract trajectories as shown
    in~\figref{vdp-abs-paths}. However, typically, the refinement by
    increasing the quantization precision requires $4$ refinement
    iterations and finally finds a concrete counter-example for
    $\epsilon=0.125$.
\end{example}
